What Can Stack Traces Tell us about of the use Exceptions in Java?

### 2014-07-07 android-stacks.tex
merging introductions - step 2

Modern applications have to cope with an increasing number of abnormal
computation states that arise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware. The exception handling
mechanism~\cite{goodenough1975exception} is one of the most used schemes for
detecting and recovering from such exceptional conditions. When an exception is
caught inside the application by the program's exception handling code, 
the application has the opportunity
to assess the conditions that caused the fault and either recover from them or abort. 
An exception that remains uncaught (is not caught by an exception handler)
leads to a program crash. In most programming languages with embedded exception handling mechanism, when a crash happens usually the language runtime 
agenerates debugging information to help
the programmer identify and fix the reason of the crash. The debugging
information is typical a stack trace, which includes an explanatory message and
the execution stack frame when the exception occurred. In Java, stack trace
consists of an ordered list of methods that were active on the call stack before
the exception occurred.

@@

The availability of exception stack traces until recently was scarce, while the
available data were only focused on few large scale projects. In the recent
past, many open source software projects have their source code and issue
repositories to Github. The concentration of projects and the existence of
projects that mine such information, such as GHTorrent~\cite{Gousi13}, made full
population studies possible.

In this work, we perform the first post mortem analysis of exception handling in
Java.  Using a custom tool called ExceptionMiner, which we develop specifically
for this study, we mine stack traces from issues across all Java projects on
GitHub. Overall, we analyzed 356,057 issues from 16,836 projects, from which
28,800 stack traces were extracted and used as a source of information for our
analysis. The stack trace analysis was augmented by additional information
extracted using byte code and source code analysis done on a carefully selected
subset of our initial sample (482 Android projects).
To guide this exploration we compiled general guidelines on how to use
exceptions proposed by Gosling~\cite{gosling2000java},
Wirfs-Brock~\cite{wirfs2006toward} and Bloch~\cite{bloch2008effective} and then
we investigate what stack traces can tell us about the adherence to such
practices in Java programs.

Some outcomes were consistently detected through
our large scale analysis of exception stack traces in the wild, such as:

@@

\subsection{Remaining Introductions :-)}

@@

For RQ1 and RQ2, we explore the domain quantitatively and highlight interesting cases by 
exploring cases qualitatively. To support this investigation, source code and bytecode 
analysis were used in combination with manual inspection to to everage the  understanding of stack traces.

>>>>

Modern applications have to cope with an increasing number of abnormal
computation states that arise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware. The exception handling
mechanism~\cite{goodenough1975exception} is one of the most used schemes for
detecting and recovering from such exceptional conditions. When an exception is thrown it can be caught inside the application (by the program's exception handling code) and the the application has the opportunity to assess the conditions that caused the fault and either recover from them or abort. 
If the exception that remains uncaught (is not caught by an exception handler) it
leads to a program crash -  uncaught exceptions ~\cite{jo2004uncaught} are one 
of the main causes of application crashes.

 In most programming languages with embedded exception handling mechanism, when a crash happens usually the language runtime generates debugging information to help
the programmer identify and fix the cause of the crash. The debugging
information is typical a stack trace, which includes an explanatory message and
the execution stack frame when the exception occurred. In Java, stack trace
consists of an ordered list of methods that were active on the call stack before
the exception occurred.

@@

The availability of exception stack traces until recently was scarce, while the
available data were only focused on few large scale projects.
Along the recent years we have witnessed a rapid increase in the number of open source 
projects that make their control version and issue tracking systems publicly 
available in repository hosting sites such as GitHub.

The concentration of open source projects and the existence of
initiatives that mine such information, such as GHTorrent~\cite{Gousi13},
 allow the information about projects to be visible within and across projects and
 make a full population studies possible.

In this work, we perform the first post mortem analysis of exception handling in
Java.  Using a custom tool called ExceptionMiner, which we develop specifically
for this study, we mine stack traces from issues across all Java projects on
GitHub. Overall, we analyzed 356,057 issues from 16,836 projects, from which
28,800 stack traces were extracted and used as a source of information for our
analysis. The stack trace analysis was augmented by additional information
extracted using byte code and source code analysis done on a carefully selected
subset of our initial sample (482 Android projects). Manual inspection was also 
used in this study to leverage the understanding of stack traces and support 
further discussions and insights.

To guide this exploration we compiled general 
guidelines on how to use exceptions proposed by Gosling~\cite{gosling2000java},
Wirfs-Brock~\cite{wirfs2006toward} and Bloch~\cite{bloch2008effective} and then
we investigate what stack traces can tell us about the adherence to such
practices in Java programs. Some outcomes were consistently detected through
our large scale analysis of exception stack traces in the wild, such as:

@@

\subsection{Tentative  Introductions to chance the focus}

@@

For RQ1 and RQ2, we explore the domain quantitatively and highlight interesting cases by 
exploring cases qualitatively. To support this investigation, source code and bytecode 
analysis were used in combination with manual inspection to leverage the  understanding of stack traces and support further discussions and insights.
